Kelompok 4_Praktikum_Pekan 8

### 2024-04-06 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
qqnorm(norm_means, main = "Normal QQ Plot", col = "#8DC16D", lwd = 5,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(norm_means, col = "red", lwd=2)

qqnorm(unif_means, main = "Uniform QQ Plot", col = "#4493CA", lwd = 5,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(unif_means, col = "red", lwd=2)

qqnorm(exp_means, main = "Exponential QQ Plot", col = "#D44155", lwd = 5,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(exp_means, col = "red", lwd=2)
```

@@

**Bangkitkan dua gugus data**

@@

```{=html}
<!-- -->
```
3.  Ambil sample dengan ukuran n = 4, 12, 20, 60, 100

>>>>

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
qqnorm(norm_means, main = "Normal QQ Plot", col = "#8DC16D", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(norm_means, col = "red", lwd=2)

qqnorm(unif_means, main = "Uniform QQ Plot", col = "#4493CA", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(unif_means, col = "red", lwd=2)

qqnorm(exp_means, main = "Exponential QQ Plot", col = "#D44155", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(exp_means, col = "red", lwd=2)
```

@@

> Bangkitkan **dua gugus data**

@@

### Normal

### Campuran

3.  Ambil sample dengan ukuran n = 4, 12, 20, 60, 100
